MG7: Configurable and scalable 16S data analysis

### 2016-07-26 docs/mg7-paper/out/paper.tex
explain the notion of best hits for a query

>>>>

All the assignment procedures work by default with input the set of
BLAST hits which have maximum bitscore among those covering the whole
query sequence; we will call this the set of best hits of a query. Note
that the criteria which determines this set of best hits is fully
configurable, adjusted to conform to its meaning in each particular
dataset: those hits which we should take into account as valid for
assignment. This is of course experiment-dependent, and we can account
for read quality or technology-specific error profiles through
configuring these criteria for the set of best hits.
